Precise predictions for same-sign W-bosons scattering at the LHC

### 2018-02-12 Draft/crosssectionLO.tex
some improvements in the draft

In Tab.~\ref{tab:wg1_LOrates}, we report the total rates at LO accuracy obtained with the set-up described in Eqs.~(\ref{cut:1}-\ref{cut:3}) with the VBS cuts $m_{\Pj\Pj} > 500 \GeV$ and $|\Delta y_{\Pj\Pj}| > 2.5$ (see Eq.~(\ref{cut:4})).
The order considered here is the order $\mathcal{O}(\alpha^6)$.
We note that several full predictions are not in statistical agreement.
These are possibly due to too aggressive estimations of statistical uncertainty or ... \MP{To be added}
Nonetheless, all these predictions agree within less than $0.5\%$.
At the level of the cross section, it seems difficult to infer the quality of the the various approximations.
This simply means that the various VBS approximations are not worth than $0.5\%$ at the level of the fiducial cross section at LO for a typical phase-space volume used by experimental collaborations.

\begin{table}[h!]
    \centering
    \begin{tabular}{c|r@{ $\pm$ }l}
      Code  &  \multicolumn{2}{c}{$\sigma[\rm{fb}]$}  \\
        \hline
        \hline
        {\sc Bonsay}  &  $X$ & $0.0002$ \\
        {\sc MG5\_aMC}&  $X$ & $0.001$  \\
        {\sc MoCaNLO+Recola}  &  $1.4347\phantom{0}$ & $0.0001$ \\
        {\sc PHANTOM} &  $1.4374\phantom{0}$ & $0.0006 $  \\
        {\sc POWHEG}  &  $1.44092$ & $0.00009$ \\
        {\sc VBFNLO}  &  $1.43796$ & $0.00005$ \\
        {\sc Whizard} &  $1.4381\phantom{0}$ & $0.0002 $
    \end{tabular}
    \caption{\label{tab:wg1_LOrates} Cross sections for the LHC process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at LO accuracy and order $\mathcal{O}(\alpha^6)$.
    The uncertainties shown refers to the estimated statistical error of the Monte Carlo programs.
    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
    \MP{Please add or check your respective numbers}}
\end{table}

>>>>

In Tab.~\ref{tab:wg1_LOrates}, we report the total rates at LO accuracy obtained with the set-up described in Eqs.~(\ref{cut:1}-\ref{cut:3}) with the VBS cuts $m_{\Pj\Pj} > 500 \GeV$ and $|\Delta y_{\Pj\Pj}| > 2.5$ (see Eq.~(\ref{cut:4})).
The order considered here is the order $\mathcal{O}(\alpha^6)$.
We note that several full predictions are not in statistical agreement. These are possibly due to Monte-Carlo 
integrators performing too aggressive estimations of statistical uncertainties. Nonetheless, all these predictions agree within less than $0.5\%$.
At the level of the cross section, it seems difficult to infer the quality of the the various approximations.
This simply means that the details of the various VBS approximations have an impact not larger than $0.5\%$ at 
the level of the fiducial cross section at LO for a typical phase-space volume used by experimental collaborations.

\begin{table}[h!]
    \centering
    \begin{tabular}{c|r@{ $\pm$ }l}
      Code  &  \multicolumn{2}{c}{$\sigma[\rm{fb}]$}  \\
        \hline
        \hline
        {\sc Bonsay}  &  $X$ & $0.0002$ \\
        {\sc MG5\_aMC}&  $1.435$ & $0.004$ TO BE UPDATED  \\
        {\sc MoCaNLO+Recola}  &  $1.4347\phantom{0}$ & $0.0001$ \\
        {\sc PHANTOM} &  $1.4374\phantom{0}$ & $0.0006 $  \\
        {\sc POWHEG}  &  $1.44092$ & $0.00009$ \\
        {\sc VBFNLO}  &  $1.43796$ & $0.00005$ \\
        {\sc Whizard} &  $1.4381\phantom{0}$ & $0.0002 $
    \end{tabular}
    \caption{\label{tab:wg1_LOrates} Cross sections for the LHC process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at LO accuracy and order $\mathcal{O}(\alpha^6)$.
    The uncertainties shown refers to the estimated statistical error of the Monte Carlo programs.
    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
    \MP{Please add or check your respective numbers}}
\end{table}

### 2018-02-12 Draft/crosssectionNLO.tex
some improvements in the draft

\begin{table}[h!]
    \centering
    \begin{tabular}{c|r@{ $\pm$ }l}
      Code  &  \multicolumn{2}{c}{$\sigma[\rm{fb}]$}  \\
        \hline
        \hline
        {\sc Bonsay}  &  $X$ & $0.0009$  \\
        {\sc MG5\_aMC}&  $X $ & $0.003$  \\
        {\sc MoCaNLO+Recola}  &  $ 1.382\phantom{0}$ & $0.002$ \\
        {\sc POWHEG}  &  $1.3556$ & $0.0009$  \\
        {\sc VBFNLO}  &  $1.3916$ & $0.0001$  \\
    \end{tabular}
    \caption{\label{tab:wg1_NLOrates} Cross sections for the LHC process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy and order $\mathcal{O}(\alpha^6)$.
    The uncertainties shown refers to estimated statistical error of the Monte Carlo programs.
    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
    \MP{Please add or check your respective numbers.}}
    \MR{My $t$-/$u$-channel-only number is $1.3703(1)$, so something additionally must be going on with Powheg, which we should comment on.}
\end{table}

>>>>

\begin{table}[h!]
    \centering
    \begin{tabular}{c|r@{ $\pm$ }l}
      Code  &  \multicolumn{2}{c}{$\sigma[\rm{fb}]$}  \\
        \hline
        \hline
        {\sc Bonsay}  &  $X$ & $0.0009$  \\
        {\sc MG5\_aMC}&  $1.363\phantom{0}$ & $0.004$  \\
        {\sc MoCaNLO+Recola}  &  $ 1.382\phantom{0}$ & $0.002$ \\
        {\sc POWHEG}  &  $1.3556$ & $0.0009$  \\
        {\sc VBFNLO}  &  $1.3916$ & $0.0001$  \\
    \end{tabular}
    \caption{\label{tab:wg1_NLOrates} Cross sections for the LHC process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy and order $\mathcal{O}(\alpha^6)$.
    The uncertainties shown refers to estimated statistical error of the Monte Carlo programs.
    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
    \MP{Please add or check your respective numbers.}}
    \MR{My $t$-/$u$-channel-only number is $1.3703(1)$, so something additionally must be going on with Powheg, which we should comment on.}
\end{table}

### 2018-02-12 Draft/description.tex
some improvements in the draft

  \item {\sc MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca} is an automatic meta-code (a code that generates codes) which makes it possible to simulate any scattering process
      including NLO QCD corrections both at fixed order and including matching to parton showers. It makes use of the FKS subtraction method~\cite{Frixione:1995ms,
        Frixione:1997np} (automated in the module {\sc MadFKS}~\cite{Frederix:2009yq,
        Frederix:2016rdc}) for regulating IR singularities. The computations of one-loop amplitudes are carried out by switching dynamically between
        two integral-reduction techniques, OPP~\cite{Ossola:2006us} or Laurent-series expansion~\cite{Mastrolia:2012bu},
        and TIR~\cite{Passarino:1978jh,Davydychev:1991va,Denner:2005nn}. These have been automated in the module {\sc MadLoop}~\cite{Hirschi:2011pa}, which
        in turn exploits {\sc CutTools}~\cite{Ossola:2007ax}, {\sc Ninja}~\cite{Peraro:2014cba,
        Hirschi:2016mdz}, or {\sc IREGI}~\cite{ShaoIREGI}, \MP{Is Collier not missing here? I think it made it to one of the default if I am correct} together with an in-house implementation of the {\sc OpenLoops} optimisation~\cite{Cascioli:2011va}.\\
        The simulation of VBS at NLO-QCD accuracy can be performed by issuing the following commands in the program interface:
\begin{verbatim}
> set complex_mass_scheme #1
> import model loop_qcd_qed_sm_Gmu #2
> generate p p > e+ ve mu+ vm j j QCD=0 [QCD] #3
> output #4
\end{verbatim}
  With these commands the complex-mass scheme is turned on {\tt \#1}, then the NLO-capable model is loaded {\tt \#2}\footnote{Despite
            the {\tt loop\_qcd\_qed\_sm\_Gmu} model also includes NLO counterterms for computing electro-weak corrections, it is not yet possible to compute such corrections
        with the current version of the code.}, finally the process code is generated {\tt \#3} (note the {\tt QCD=0} syntax to select the purely-electroweak process)
        and written to disk {\tt \#4}. Because of some internal limitations, which will be lifted in the future version capable of computing both QCD and EW corrections,
        only loops with QCD-interacting particles are generated.
        \MP{Detail of the approximation done, divergent part, assumed to cancel etc.}

>>>>

  \item {\sc MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca} is an automatic meta-code (a code that generates codes) which makes it possible to simulate any scattering process
      including NLO QCD corrections both at fixed order and including matching to parton showers. It makes use of the FKS subtraction method~\cite{Frixione:1995ms,
        Frixione:1997np} (automated in the module {\sc MadFKS}~\cite{Frederix:2009yq,
        Frederix:2016rdc}) for regulating IR singularities. The computations of one-loop amplitudes are carried out by switching dynamically between
        two integral-reduction techniques, OPP~\cite{Ossola:2006us} or Laurent-series expansion~\cite{Mastrolia:2012bu},
        and TIR~\cite{Passarino:1978jh,Davydychev:1991va,Denner:2005nn}. These have been automated in the module {\sc MadLoop}~\cite{Hirschi:2011pa}, which
        in turn exploits {\sc CutTools}~\cite{Ossola:2007ax}, {\sc Ninja}~\cite{Peraro:2014cba,
        Hirschi:2016mdz}, {\sc IREGI}~\cite{ShaoIREGI}, or {\sc Collier}~\cite{Denner:2016kdg}, together with an in-house 
        implementation of the {\sc OpenLoops} optimisation~\cite{Cascioli:2011va}. Finally, scale and PDF uncertainties can be obtained in an exact manner via reweigthing
        at zero additional CPU cost~\cite{Frederix:2011ss}.\\
        The simulation of VBS at NLO-QCD accuracy can be performed by issuing the following commands in the program interface:
\begin{verbatim}
> set complex_mass_scheme #1
> import model loop_qcd_qed_sm_Gmu #2
> generate p p > e+ ve mu+ vm j j QCD=0 [QCD] #3
> output #4
\end{verbatim}
  With these commands the complex-mass scheme is turned on {\tt \#1}, then the NLO-capable model is loaded {\tt \#2}\footnote{Despite
            the {\tt loop\_qcd\_qed\_sm\_Gmu} model also includes NLO counterterms for computing electro-weak corrections, it is not yet possible to compute such corrections
        with the current version of the code.}, finally the process code is generated {\tt \#3} (note the {\tt QCD=0} syntax to select the purely-electroweak process)
        and written to disk {\tt \#4}. Because of some internal limitations, which will be lifted in the future version capable of computing both QCD and EW corrections,
        only loops with QCD-interacting particles are generated. As it has been already mentioned, such an approximation is equivalent to the assumption that the finite part of
        those loops which feature EW bosons is zero. In practice, since a part of the contribution to the single pole is also missing, the internal 
        pole-cancelation check at run time has to be turned off, by setting the value of the {\tt IR\-Pole\-Check\-Threshold} and 
        {\tt Precision\-Virtual\-At\-Run\-Time} parameters in the {\tt Cards/FKS\_params.dat} file to -1.

### 2018-02-12 Draft/shower.tex
some improvements in the draft

\begin{table}[h!]
    \centering
    \begin{tabular}{c|r@{ $\pm$ }l}
      Code  &  \multicolumn{2}{c}{$\sigma[\rm{fb}]$}  \\
        \hline\hline
        {\sc MG5\_aMC}+{\sc Pythia8}&  $1.450 (1.368)$ & $0.004$  \\
        {\sc MG5\_aMC}+{\sc Herwig++}&  $1.445 (1.363)$ & $0.004$  \\
        {\sc POWHEG}  &  $1.3642$ & $0.0004$  \\
        {\sc VBFNLO}+{\sc Herwig7-Dipole} &  $1.3389$ & $0.0006$  \\
        {\sc VBFNLO}+{\sc Herwig7-Default} &  $1.3067$ & $0.0006$  \\
        \hline
        {\sc MG5\_aMC}+{\sc Pythia8} (LO)&  $1.352 (1.275)$ & $0.003$  \\
        {\sc MG5\_aMC}+{\sc Herwig++} (LO)&  $1.343 (1.267)$ & $ 0.003$  \\
        {\sc PHANTOM}+{\sc Pythia8} &  $1.235\phantom{0} $ & $0.001$  \\
        {\sc PHANTOM}+{\sc Herwig++} &  $1.260\phantom{0} $ & $0.001$  \\
        {\sc VBFNLO}+{\sc Herwig7} (LO) &  $1.3001$ & $0.0002$  \\
    \end{tabular}
    \caption{\label{tab:PSrates} Rates at NLO-QCD (LO-QCD) accuracy matched to parton shower within VBS cuts obtained with the different codes used in this comparison,
    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process. Numbers in parentheses for the {\sc MG5\_aMC} simulations
    are rescaled to account for the effect related to the boson widths computed by {\sc MadSpin} (see the text for details).}
\end{table}

>>>>

\begin{table}[h!]
    \centering
    \begin{tabular}{c|r@{ $\pm$ }l}
      Code  &  \multicolumn{2}{c}{$\sigma[\rm{fb}]$}  \\
        \hline\hline
        {\sc MG5\_aMC}+{\sc Pythia8}&  $1.450 \, (1.368)$ & $0.004$  \\
        {\sc MG5\_aMC}+{\sc Herwig++}&  $1.445 \, (1.363)$ & $0.004$  \\
        {\sc POWHEG}  &  $1.3642$ & $0.0004$  \\
        {\sc VBFNLO}+{\sc Herwig7-Dipole} &  $1.3389$ & $0.0006$  \\
        {\sc VBFNLO}+{\sc Herwig7-Default} &  $1.3067$ & $0.0006$  \\
        \hline
        {\sc MG5\_aMC}+{\sc Pythia8} (LO)&  $1.352 \, (1.275)$ & $0.003$  \\
        {\sc MG5\_aMC}+{\sc Herwig++} (LO)&  $1.343 \, (1.267)$ & $ 0.003$  \\
        {\sc PHANTOM}+{\sc Pythia8} &  $1.235\phantom{0} $ & $0.001$  \\
        {\sc PHANTOM}+{\sc Herwig++} &  $1.260\phantom{0} $ & $0.001$  \\
        {\sc VBFNLO}+{\sc Herwig7} (LO) &  $1.3001$ & $0.0002$  \\
    \end{tabular}
    \caption{\label{tab:PSrates} Rates at NLO-QCD (LO-QCD) accuracy matched to parton shower within VBS cuts obtained with the different codes used in this comparison,
    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process. Numbers in parentheses for the {\sc MG5\_aMC} simulations
    are rescaled to account for the effect related to the boson widths computed by {\sc MadSpin} (see the text for details).}
\end{table}
